---
title: "Sepsis Report"
format: html
output: html_document
execute: 
  eval: true
  echo: true
  warning: false
  message: false
editor: visual
---

```{r,echo=FALSE,message=FALSE}
library(googledrive)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(lubridate)
library(timeDate)
library(purrr)
library(patchwork)
library(DT)
```

This report was created by **Bibin Joseph** on `r format(Sys.time(), '%A, %B %d, %Y at %I:%M %p')`.

Reading the Latest physiological data from `Google Drive`

```{r,message=FALSE}
file_link <- "https://drive.google.com/file/d/1bloQHuPsZIhTZTnqeYkj15W_gSmKtHOd"
ICU_data <- drive_read_string(file_link) %>% 
  read_delim(",")

```

Removing the `NA` values form the Data

```{r}

ICU_data_clean<-na.omit(ICU_data)

```

Identify patients with sepsis and Creating the **for Patients with Sepsis**

```{r}

Sepsis_Patients<-ICU_data_clean %>% 
  group_by(PatientID) %>% 
  filter(SepsisLabel == 1 & ICULOS == max(ICULOS)) %>% 
  select(PatientID, HR, Temp, Resp)

```

`Table.1` Patients who currently have sepsis (if any), along with their most recent heart rate, temperature, and respiratory rate

```{r,echo=FALSE}
kable(Sepsis_Patients)
```

Plots for all patients who have sepsis (if any) that show the complete history of their heart rate, temperature, and respiratory rate during their time in the ICU

```{r,warning=FALSE}

# Subset the data to include only patients with sepsis
sepsis_data <- ICU_data %>% filter(SepsisLabel == 1)

# Group the data by PatientID
sepsis_data <- sepsis_data %>% group_by(PatientID)

# Create a function to plot heart rate, temperature, and respiratory rate for a single patient
plot_patient <- function(patient_data) {
  ggplot(patient_data, aes(x = obsTime)) +
    geom_line(aes(y = HR, color = "Heart Rate")) +
    geom_line(aes(y = Temp, color = "Temperature")) +
    geom_line(aes(y = Resp, color = "Respiratory Rate")) +
    labs(x = "Time", y = "Measurement", color = "Variable") +
    ggtitle(paste0("Patient ", unique(patient_data$PatientID))) +
    theme_bw()
}

# Create a list of plots for each patient with sepsis
patient_plots <- sepsis_data %>% 
  group_split() %>% 
  map(plot_patient)

# Arrange the plots in a grid

wrap_plots(patient_plots, ncol = 2, width = 12, height = 8) 



```

`Table.2` showing the *change* in heart rate, temperature, and respiratory rate between the last two measurements for all patients

```{r}

ICU_diff<-ICU_data %>%
  group_by(PatientID) %>%
  summarise(`Temperature Difference` = last(Temp) - Temp[n()-1],
            `Heart Rate Difference` = last(HR) - HR[n()-1],
           `Respiratoy Rate Difference` = last(Resp) - Resp[n()-1])

datatable(ICU_diff, 
          options = list(pageLength = 10, searching=TRUE),
          filter = 'top')

```
